---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Load the data found in the "activity.zip" file (assumption that this file already exists in the root of this project).
```{r}
if(file.exists("activity.zip")){
    dataFile <- unz("activity.zip", "activity.csv")
    data <- read.csv(dataFile, header = TRUE)
}
```

There are a number of days/intervals where there are "NA" step values. For now we'll clean this up from the dataset

```{r}
data <- data[!is.na(data$steps), ]
```

## What is mean total number of steps taken per day?

Since each day comprises of multiple intervals, we'll sum the number of steps taken each day

```{r}
library(dplyr)
stepsPerDay <- summarise(group_by(data, date), steps=sum(steps))
```

From the histogram below we can visualize the number of steps taken each day

```{r}
library(ggplot2)
ggplot(stepsPerDay, aes(x=date, y = steps)) + geom_histogram(stat="identity", binwidth=30, colour="white") + theme(axis.text.x = element_text(angle=90)) + ylab("Steps") + xlab("Date") 
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
